\documentclass[a4paper]{article}

\usepackage{fullpage} % Package to use full page
\usepackage{parskip} % Package to tweak paragraph skipping
\usepackage{tikz} % Package for drawing
\usepackage{amsmath}
\usepackage{hyperref}

\title{CSCI335: Software Analysis and Design III}
\author{Project \#1}
\date{Due Date: June 10th, 2025}

\begin{document}
\maketitle


\section*{Problem 1}
Create a class for a dynamic(on the heap) 3 by 3 matrix(using arrays and not vectors) named \texttt{Matrix33}:
\begin{enumerate}
    \item Make sure the private attribute is a \textbf{dynamically allocated} 2d array
    \item Add a default constructor that takes no arguments and does nothing in the body: \begin{verbatim}
        matrix33(){}
    \end{verbatim}
    \item Make sure to separate the interface and implementation
    \item A constructor that accepts a 2d array as an input parameter
    \item Write a copy constructor
    \item Write a move constructor
    \item Write a copy assignment 
    \item Write a move assignment
    \item Overload * operator for matrix multiplication
    \item Overload * operator for scalar multiplication
    \item Overload + operator for matrix addition
    \item Overload $<<$ operator to print matrix
    \item Overload $>>$ operator, and prompt user to enter 9 consecutive values
    \item Write a function to compute the determinant of the matrix
    \item For each of the functions above(number 3-14) tell me the big O run time and space time of your algorithm with an explanation. 
\end{enumerate}
\newpage

\section*{Problem 2}
\begin{itemize}
    \item Given the Vector class in this directory, create a separate main.cpp file where you include the headers for \texttt{Matrix33} and \texttt{Vector3}
    \item Overload the operator (), for accessing the private attributes of the \texttt{Vector3} and \texttt{Matrix33} classes.
    \begin{verbatim}
        double operator()(int row, int col)
        {
            return matrix[row][col];
        }
    \end{verbatim} 
    \item Write a function in main.cpp that takes a  \texttt{Matrix33}=A and \texttt{Vector3}=x as input parameters
          and computes Ax=b, and returns a type of \texttt{Vector3}(b). What is the the big O runtime and time complexity of function? Explain. 
    \item prompt the user to enter a matrix(3 by 3) and vector(3), then call your function to compute the product, then print the result.
\end{itemize}
\newpage
 

\section*{Problem 3}
Do problem 1, but for an n by m matrix using the vector template class(stl). 
In the constructor add the parameters for the number of rows (n) and number of columns(m).


\end{document}